\papertitle

### 2021-03-05 source_separation/paper/paper.tex
added title
typos in abstract

% Title.
% ------
\def\papertitle{Paper Title}

% Authors
% Please note that submissions are NOT anonymous, therefore 
% authors' names have to be VISIBLE in your manuscript. 
% Authors are entered as an ordered list, each one can be linked to multiple affiliations using the correct index.
% Available tags for authors are: \firstname \middlename \lastname \generation \originalname \email \orcid
% Available tags for affiliations are: \unit \department \institution \streetaddress \city \state \postcode \country \type
% type can take as value: University, Company, Music, Independent, Other
%
% \author[]{\mbox{\firstname{}\middlename{}\lastname{}\originalname{}\generation{}\email{}\orcid{}}}
% mbox force an author not to be split over multiple lines
\author[1]{\mbox{\firstname{Carmine}\lastname{Cella}}}
\author[1]{\mbox{\firstname{Luke}\lastname{Dzwonczyk}}}

%%Affiliations
\affil[1]{\department{Center for New Music and Audio Technologies}\institution{University of California, Berkeley}\city{Berkeley}\state{California}\country{USA}\affiliationtype{University}}

@@

	\begin{abstract}
		In this paper, we will study the possibility of adding source separation as a pre-processing step to the orchestration process. We first discuss the motivation of this addition and its effect on the quality of orchestrations of multi-layered sounds. Second, we select several state-of-the-art models for both music source separation (separation of instruments) and universal sound separation (separation of arbitrary sounds of different types), and compare their effectiveness for the task of orchestration. We assessed which methods best suit the needs of orchestration by applying them on hand picked target sounds, orchestrating the separated outputs, and finally comparing them to the orchestration of the same target without separation. Our experiments show that the quality of orchestrations improved, both qualitatively and quantitatively, indicating that our approach is promising. Finally, we discuss the interest of unsupervised methods compared to supervised methods in the case of assisted orchestration, where data is relatively scarce.
	\end{abstract}
	%

>>>>

% Title.
% ------
\def\papertitle{Source separation methods for computer-assisted orchestration}

% Authors
% Please note that submissions are NOT anonymous, therefore 
% authors' names have to be VISIBLE in your manuscript. 
% Authors are entered as an ordered list, each one can be linked to multiple affiliations using the correct index.
% Available tags for authors are: \firstname \middlename \lastname \generation \originalname \email \orcid
% Available tags for affiliations are: \unit \department \institution \streetaddress \city \state \postcode \country \type
% type can take as value: University, Company, Music, Independent, Other
%
% \author[]{\mbox{\firstname{}\middlename{}\lastname{}\originalname{}\generation{}\email{}\orcid{}}}
% mbox force an author not to be split over multiple lines
\author[1]{\mbox{\firstname{Luke}\lastname{Dzwonczyk}}}
\author[1, 2]{\mbox{\firstname{L\'eo}\lastname{Chedin}}}
\author[1]{\mbox{\firstname{Alejandro}\lastname{Saldarriaga-Fuertes}}}
\author[1]{\mbox{\firstname{Max}\lastname{Sherr}}}
\author[1]{\mbox{\firstname{H\'el\`ene-Camille}\lastname{Crayencour}}}
\author[1]{\mbox{\firstname{Carmine-Emanuele}\lastname{Cella}}}

%%Affiliations
\affil[1]{\department{Center for New Music and Audio Technologies}\institution{University of California, Berkeley}\city{Berkeley}\state{California}\country{USA}\affiliationtype{University}}
\affil[2]{\department{ENS}\institution{}\city{Paris}\state{}\country{France}\affiliationtype{University}}

@@

	\begin{abstract}
		In this paper, we will study the possibility of adding source separation as a pre-processing step to the computer-assisted orchestration process. We first discuss the motivation of this addition and its effect on the quality of orchestrations of multi-layered sounds. Second, we select several state-of-the-art models for both music source separation (separation of instruments) and universal sound separation (separation of arbitrary sounds of different types), and compare their effectiveness for the task of orchestration. We assessed which methods best suit the needs of orchestration by applying them on hand picked target sounds, orchestrating the separated outputs, and finally comparing them to the orchestration of the same target without separation. Our experiments show that the quality of orchestrations improved, both qualitatively and quantitatively, indicating that our approach is promising. Finally, we discuss the interest of unsupervised methods compared to supervised methods in the case of assisted orchestration, where data is relatively scarce.
	\end{abstract}
	%
